EoS-insensitive relations after GW170817

### 2019-01-16 paper/bin-love-after-gw170817.tex
added comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state, or EoS) of cold supranuclear matter, accessible in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately EoS-insensitive ``binary Love EoS insensitive relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" EoS insensitive relations.
% What universal relations do
Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing parameter extraction uncertainties.
% What we will do
However, even the most precise of EoS insensitive relations carry EoS variation which inject systematic errors into the parameter extraction process.
In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love EoS-insensitive relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
However, we show that the systematic effects of these relations is very small until next-generation detectors. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future design upgrade Voyager.
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
%Intro
The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?} {\ny{Look up the PREX and CREX experiments at JLab (a good author is Horowitz, e.g. Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}}), making NSs ideal laboratories for constraining ultra dense nuclear matter.

@@

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.  
Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
Similar ``I-Love-Q" and ``C-Love" EoS-insensitive relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
However, these EoS-insensitive relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.

%How we improved this
In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love EoS-insensitive relations.
We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining if the uncertainties can be reduced.
In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
To estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}

\subsection{Executive Summary}
\zc{Me and Kent discussed whether or not we should include this section or not, and we decided like having the quick summary for busy readers - especially with the increasing number of figs and tables (8 tables, 14 figures so far). We can discuss this further if anyone doesn't want it included :)}
{\ny{I'm ok with keeping this, but let's get the science finished first.}}
%What we did
In this paper we attempt to improve I-Love-Q, C-Love, and binary Love EoS-insensitive relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love EoS-insensitive relations.
Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.

@@

Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love EoS-insensitive relations, with sightly increased EoS variability.

@@

It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love EoS-insensitive relations will become necessary.

@@

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love EoS-insensitive relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
We next examine these improved EoS-insensitive relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

\subsection{EoS insensitive relations}\label{sec:eosInsensitive}
Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
\begin{equation}
\Lambda_s \equiv \frac{\Lambda_1 + \Lambda_2}{2}, \hspace{6mm} \Lambda_a \equiv \frac{\Lambda_1 - \Lambda_2}{2},
\end{equation}
display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
It was shown through a simple Fisher analysis that the use of binary Love EoS-insensitive relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.

@@

{\ny{Overall, let's not call these relations ``I-Love-Q EOS insensitive relations'' or ``binary love EOS insensitive relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature). It should be clear when we define them that they are EOS insensitive}}

@@

\begin{table*}
\centering
\caption{
Updated fit parameters for the I-Love-Q EoS-insensitive relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
}\label{tab:ILQfit}
\begin{tabular}{ c  c | c c c c c } 
 \hline
 \hline
 $y_i$ & $x_i$ & $a_i$ & $b_i$ & $c_i$ & $d_i$ & $e_i$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $1.4934168$ & $0.0640972$ & $0.0208513$ & $-5.018022 \times 10^{-4}$ & $3.1638958 \times 10^{-7}$ \\
 $\bar{Q}$ & $\Lambda$ & $0.2092931$ & $0.0740442$ & $-0.0538210$ & $-5.018022 \times 10^{-3}$ & $1.576165 \times 10^{-4}$ \\ 
  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
 \hline
 \hline
\end{tabular}
\end{table*}

\begin{table*}
\centering
\caption{
I-Love-Q, C-Love, and R-Love EoS-insensitive relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
 $R$ & $\Lambda$ & $-1/40$ & $8.5752160$ & $-10.5478546$ & $17.3202891$ & $-29.7572150$ & $-9.9777952$ & $21.9091242$ & $-31.7691648$\\
\hline
\hline
\end{tabular}
\end{table*}

Fig.~\ref{fig:ILQ} shows the improved I-Love EoS-insensitive relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q EoS-insensitive relation.

\begin{figure*}
\begin{center} 
\includegraphics[width=.32\textwidth]{IL.eps}
\includegraphics[width=.32\textwidth]{QL.eps}
\includegraphics[width=.32\textwidth]{IQ.eps}
\end{center}
\caption{
Individual I-Love EoS-insensitive relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green).
}
\label{fig:ILQ}
\end{figure*}

@@

Observe how the hybrid star EoSs do obey the I-Love-Q EoS-insensitive relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q EoS-insensitive relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.

{\ny{This is a bit strange, but probably still correct. But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality. Why is this?}}

{\ny{UP TO HERE}}

\subsection{C-Love Relations}\label{sec:clove}
In this section we consider approximate C-Love EoS-insensitive relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.

@@

\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
In this section, we consider the effect of hybrid star EoSs on the C-Love EoS-insensitive relation.
Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state, or EoS) of cold supranuclear matter, accessible in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately EoS-insensitive ``binary Love relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of EoS-insensitive relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" relations.
% What universal relations do
Such EoS-insensitive relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing parameter extraction uncertainties.
% What we will do
However, even the most precise of EoS insensitive relations carry EoS variation which inject systematic errors into the parameter extraction process.
In this document, we explain how one can reduce equation of state variation for I-Love-Q, C-Love, and binary Love relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers.
However, we show that the systematic effects of these relations is very small until next-generation detectors. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these EoS-insensitive relations with future gravitational wave observations.
We conclude that the systematic errors injected from the use of improved EoS-insensitive relations become comparable to the statistical errors for future design upgrade Voyager.
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
%Intro

{\ny{Just some general comments so that we don't forget:
\begin{itemize}
\item The EoS-insensitive relations are called ``binary Love'', ``I-Love-Q'', ``C-Love'' and ``R-Love.'' There is no need to call them ``binary Love EoS-insensitive relations.'' That's too verbose and not what they are called in the literature. I am ok with describing these relations as EoS-insensitive instead of approximately universal, but let's not change the names. 
\item There is some serious tidying up that needs to be done to all of the text. Specifically, there are missing prepositions, like ``the'', in lots of places that makes the reading a bit choppy and we can improve. Zack, when you have a chance, please do a detail read through and fix the flow as much as you can. 
\item Eventually, we need to discuss the abstract and the intro in more detail. 
\item Let's not forget to check the acknowledgements for funding sources. 
\item Let's do a spell check. 
\item Let's remove all commented out text.  
\end{itemize}
}}
The dependence of pressure on density for cold supranuclear matter found inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS to around the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy} (although some temperature-dependent heavy-ion collision experiments may probe higher densities \zc{Katerina do you know of any papers on this?} {\ny{Look up the PREX and CREX experiments at JLab (a good author is Horowitz, e.g. Abrahamyan:2012gp, Horowitz:2012tj, Horowitz:2013wha)}}), making NSs ideal laboratories for constraining ultra dense nuclear matter.

@@

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\lambda_0$.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\Lambda_{s,a}=\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction of $\Lambda_s$ on the removal of parameter $\Lambda_a$ from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.  
Use of these relations leads to up to an order of magnitude improvement in parameter estimation of $\Lambda_s$ through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
Similar ``I-Love-Q" and ``C-Love" relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.
However, these EoS-insensitive relations have been tuned to a collection of EoS models, and each have intrinsic uncertainties associated with their use.

%How we improved this
In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for I-Love-Q, C-Love, and binary Love relations.
We also investigate the relationship between the NS radius and its tidal deformability, or the R-Love relations, determining if the uncertainties can be reduced.
In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
Further, we estimate the viability of using improved EoS-insensitive relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.
To estimate the effect of waveform mismodeling, we additionally consider two different tidal corrections to the injected PhenomD~\cite{PhenomDI,PhenomDII} waveform: 6PN~\cite{Wade:tidalCorrections} and NRTidal~\cite{Samajdar:NRTidal}

\subsection{Executive Summary}
\zc{Me and Kent discussed whether or not we should include this section or not, and we decided like having the quick summary for busy readers - especially with the increasing number of figs and tables (8 tables, 14 figures so far). We can discuss this further if anyone doesn't want it included :)}
{\ny{I'm ok with keeping this, but let's get the science finished first.}}
%What we did
In this paper we attempt to improve I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in EoS-insensitive relations.

@@

Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.

@@

It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.

@@

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love relations, and considering how well hybrid star EoSs agree with the EoS-insensitive relations.
We next examine these improved EoS-insensitive relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

\subsection{EoS insensitive relations}\label{sec:eosInsensitive}
Current gravitational wave interferometry is not yet sensitive enough to accurately extract both tidal parameters $\tilde{\Lambda}$ and $\delta\tilde{\Lambda}$.
In a search to remedy this, Yagi and Yunes~\cite{Yagi:binLove} found that symmetric and antisymmetric combinations of tidal deformabilities:
\begin{equation}
\Lambda_s \equiv \frac{\Lambda_1 + \Lambda_2}{2}, \hspace{6mm} \Lambda_a \equiv \frac{\Lambda_1 - \Lambda_2}{2},
\end{equation}
display EoS-insensitive properties to a high degree, showing EoS variations up to 20\% for binaries with masses less than $1.7 \text{ M}_{\odot}$, for a representative set of 11 EoSs. 
These ``binary Love relations" allow one to break degeneracies between coupled tidal parameters.
This is important for two reasons: (i) allows us to algebraically eliminate tidal parameters from the template parameter list, improving parameter estimation, and (ii) automatic measurement of second tidal parameter given observation of the first.
It was shown through a simple Fisher analysis that the use of binary Love relations improved parameter extraction on $\tilde{\Lambda}$ by an order of magnitude.

@@

{\ny{Overall, let's not call these relations ``I-Love-Q relations'' or ``binary love relations.''  It's much better to be brief and simply call them I-Love-Q relations and Binary Love relations (like is done in the literature). It should be clear when we define them that they are EOS insensitive}}

@@

\begin{table*}
\centering
\caption{
Updated fit parameters for the I-Love-Q relations, fitted to the constrained EoS data by the curve found in Eq.~\ref{eq:ILQfit}.
}\label{tab:ILQfit}
\begin{tabular}{ c  c | c c c c c } 
 \hline
 \hline
 $y_i$ & $x_i$ & $a_i$ & $b_i$ & $c_i$ & $d_i$ & $e_i$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $1.4934168$ & $0.0640972$ & $0.0208513$ & $-5.018022 \times 10^{-4}$ & $3.1638958 \times 10^{-7}$ \\
 $\bar{Q}$ & $\Lambda$ & $0.2092931$ & $0.0740442$ & $-0.0538210$ & $-5.018022 \times 10^{-3}$ & $1.576165 \times 10^{-4}$ \\ 
  $\bar{I}$ & $\bar{Q}$ & $1.3832702$ & $0.5931020$ & $-0.0216132$ & $0.0419044$ & $-2.9676365 \times 10^{-3}$ \\
 \hline
 \hline
\end{tabular}
\end{table*}

\begin{table*}
\centering
\caption{
I-Love-Q, C-Love, and R-Love relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $K_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
 $C$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
 $R$ & $\Lambda$ & $-1/40$ & $8.5752160$ & $-10.5478546$ & $17.3202891$ & $-29.7572150$ & $-9.9777952$ & $21.9091242$ & $-31.7691648$\\
\hline
\hline
\end{tabular}
\end{table*}

Fig.~\ref{fig:ILQ} shows the improved I-Love relations between the dimensionless moment of inertia $\bar{I} \equiv I/M^3$, the dimensionless quadrupole moment $\bar{Q} \equiv Q/M^3$, and the dimensionless tidal deformability $\Lambda$ for both the constrained and unconstrained sets of EoSs (each with individual fits pertaining to only that set of EoSs {\ny{I think we should here say which fit we are using (I think you are using the new one.)}}).
We observe that the constrained EoSs show considerable improvement from both the results of previous works~\cite{Yagi:ILQ}, and from the unconstrained EoSs.
This is further validated in Tab.~\ref{tab:maxVar}, where the maximal EoS variation from each fit is tabulated; comparing the results of previous works to the unconstrained, and constrained sets of EoSs.
Observe how the constrained EoSs outperform both other cases by a considerable amount for each I-Love-Q relation.

\begin{figure*}
\begin{center} 
\includegraphics[width=.32\textwidth]{IL.eps}
\includegraphics[width=.32\textwidth]{QL.eps}
\includegraphics[width=.32\textwidth]{IQ.eps}
\end{center}
\caption{
Individual I-Love relations $\bar{I}-\Lambda$ (left), $\bar{Q}-\Lambda$ (center), and $\bar{I}-\bar{Q}$ (right), shown for both the constrained EoSs (solid green) and unconstrained EoSs (dotted maroon).
In these figures, the black dashed lines corresponds to the fits given by Eq.~\ref{eq:ILQfitNew} (note: each panel contains individual fits for the constrained and unconstrained EoSs, indistinguishable on such a large scale).
Observe how the fractional difference from the fits, shown in the bottom panels, is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:ILQ}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the fractional difference from the nuclear matter fits for the 10 hybrid star EoSs (dashed green). {\ny{These figures are all too heavy and they make the scrolling of the pdf difficult. Can you downgrade their resolution or save them as pdf please?}}
}
\label{fig:ILQ}
\end{figure*}

@@

Observe how the hybrid star EoSs do obey the I-Love-Q relations up to $\sim1.7$\%, slightly higher than that found here for nuclear matter EoSs, as well as that found in previous works~\cite{Yagi:ILQ}.
Further, we observe that the universality can not be improved by much through the introduction of new fits, only bringing the max EoS variation down to $\sim1$\% for the fits constructed with only hybrid star EoSs.
Concluding, we claim that hybrid star EoSs \emph{do} obey the I-Love-Q relations computed through nuclear EoS data, but the lack of universality goes up to $\sim1.7$\%.

{\ny{This is a bit strange, but probably still correct. But ``this'' I mean the fact that when you fit only to the hybrid stars you do not get better than $1\%$ universality. If I look at the hybrid curves alone, they look like the same simple lines as in the neutron star case (but of course a $1\%$ difference wouldn't show on this scale). Why is it that we can lower fractional difference in the NS case but not in the hybrid case?}}

{\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only? (ie. the analogous thing to the green dashed lines of the figure below, but also with the fits to the total set, to just the hybrids and to just the neutron stars.) I wonder whether there is any improvement at all when you fit just to hybrid stars or whether there are any features.}}

\subsection{C-Love Relations}\label{sec:clove}
In this section we consider approximately EoS-insensitive C-Love relations between NS compactness $C \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
In addition, we show the R-Love relations, giving the relationship between NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.

@@

\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
In this section, we consider the effect of hybrid star EoSs on the C-Love relation.
Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.

Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
From this, we similarly conclude that hybrid stars do obey the C-Love relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
We observe similar results for the case of R-Love relations, as seen by the dashed green curves in Fig.~\ref{fig:rlove}.
Here, the hybrid stars show a maximal fractional difference of $30.82\%$ when compared to the constrained EoS fits - a value much smaller than the unconstrained EoSs variation.

{\ny{let's in general drop the sig figs everywhere, e.g. in 30.82 percent.}}
